Trends of SDR in Thessaloniki

### 2023-06-09 Article.Rmd
Commit 2023-06-09 10:17

## Data process.

<!-- ### Data selection -->
Due to a significant measurement uncertainty near, the horizon, we have to exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1 \text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @TSIStsi (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).
As a result, we can analyze all radiation data as a fraction of Sun's TSI.

## Process and aggregation of radiometric data

In this study, we present any radiometric data as a percent departure from the corresponding seasonal mean.
When we use daily aggregated data we compute the mean values for the day and exclude instances with less than `r Daily_aggregation_N_lim` valid data points.
Accordingly, monthly values are computed from the daily aggregated data, month with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values are computed based on the day of year number and the monthly by the calendar month.

>>>>

## Data and data selection.

<!-- ### Data selection -->
Due to a significant measurement uncertainty near, the horizon, we have to exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we excluded data with Azimuth angle between 
$35^\circ$ and $120^\circ$ with SZA greater than $80^\circ$.
On the latter instances, Sun is systematically, not visible by the instrument's location.
<!-- 1au -->
To make the measurements comparable throughout the dataset, we adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
Subsequently, we made all measurements relative to the Total Solar Irradiance (TSI) at $1 \text{au}$, in order to compensate for the Sun's intensity variability, using a homogenized time series of satellite TSI observations.
The TSI data we use, is a combination of data from NOAA [@Coddington2005] (for `r as.Date(TSIinfo[TSI_Source == "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source == "NOAA", End])`) and adjusted data from @TSIStsi (for `r as.Date(TSIinfo[TSI_Source != "NOAA", Start])` - `r as.Date(TSIinfo[TSI_Source != "NOAA", End])`).
As a result, we can present all radiation data as a fraction of Sun's TSI.

### Aggregation of radiometric data

Before further analysis, we implement an appropriate aggregation scheme on the 1-minute data, to preserve the ....representabiliyt....
When we use daily mean values we exclude instances with less than `r Daily_aggregation_N_lim` valid data points.
Accordingly, monthly values are computed from the daily aggregated data, where months with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values are indexed based on the day of year number, and the monthly by the corresponding calendar month.
